---
title: "Exercise_3"
author: "Zijing He"
date: "4/5/2019"
output: md_document
---

## Question 1

```{r, echo=FALSE,include=FALSE}
library(RCurl)
x <- getURL("https://raw.githubusercontent.com/ZijingHe/hello-world/master/data/greenbuildings.csv")
greenbuildings <- read.csv(text = x)

library(tidyverse)
library(mosaic)
library(foreach)
library(doMC)  # for parallel computing

green<-na.omit(greenbuildings)
### forward selection
lm0 = lm(Rent ~ 1, data=green)
lm_forward = step(lm0, direction='forward',
                  scope=~(green_rating + size+empl_gr+leasing_rate+stories+age+renovated+class_a+class_b+net+amenities+cd_total_07+hd_total07+Precipitation+Gas_Costs+Electricity_Costs+cluster_rent)^2)

### step selection
lm_median = lm(Rent ~ green_rating + size+empl_gr+leasing_rate+stories+age+renovated+ class_a+class_b+net+amenities+cd_total_07+hd_total07+Precipitation+Gas_Costs+Electricity_Costs+cluster_rent, data = green)
lm_step = step(lm_median, 
               scope=~(.)^2)

### backward selection 
lm_big = lm(Rent ~ (green_rating + size+empl_gr+leasing_rate+stories+age+renovated+ class_a+class_b+net+amenities+cd_total_07+hd_total07+Precipitation+Gas_Costs+Electricity_Costs+cluster_rent)^2, data = green)
lm_backward = step(lm_big, direction='backward',
                   scope = ~ 1)

```

```{r, echo=FALSE}
# what variables are included?
getCall(lm_step)
coef(lm_step)
```

1. I use green rating as indicator of green certified, which equals 1 when building is either LEED or Energystar. To figure out the best predictive model, I use forward selection method, step selection and backward selection, then, choose the model with the smallest AIC. For backward selection, the final model does not include green rate; comparing AIC between forward model(AIC=34512.51) and step model (AIC=34407.55), step model should be the best one.

2. With and without green certification will change the average rental income per square foot, holding all else fixed, by 1.24 - 2.08 x amenities, which means the effect depends on whether amenities is available on-site. Although, in the step predictive model, there are interactions between age and green rating, the magnitude is quite small.

3. The effect is different for buildings with amenities on-site and without amenities. On average, the effect is larger for buildings without amenities. The difference is around 2.08 on average. 

## Question 2
### (1)
There is simultaneity problem, which causes endogeneity of police with respect to crime rate. It is hard distinguish whether the change of crime rate cause the change of police or the change of police cause the change of crime rate. For example, high crime rates are likely to increase marginal productivity of police. Places with an inordinate amount of crime, therefore, tend to employ a large police force, even if police reduce crime. Thus, simple linear regression by using data from different cities will generate biased estimators.

### (2)
They wanted a variable which is unrelated to crime, but causes the change of police, and they found the terrorism alert level was a great case. By law, since Washington, D.C., is likely to be a terrorism target, when the terror alert level goes to orange, then extra police are put on the Mall and other parts of Washington to protect against terrorists. It has nothing to do with street crime or things like that. From table 2 column 1, the coefficient on the alert level is statistically significant at the 5 percent level and indicates that on high-alert days, total crimes decrease by an average of seven crimes per day, or approximately 6.6 percent. 
Also, they considered that it was possible that tourists were less likely to visit Washington or to go out on high-alert day, which mean there were going to be less victims on the street.  From table 2 column 2, they verify that high-alert levels are not being confounded with tourism levels by including logged midday Metro ridership directly in the regression. 

### (3)
They considered that it was possible that tourists were less likely to visit Washington or to go out on high-alert day, which mean there were going to be less victims on the street. To control metro ridership, they can check the hypothesis that whether high-alert levels are confounded with tourism levels or not.

###(4)
Table 4 tests whether police increase in one district will decrease/affect police presence in other districts. If so, they would expect to see higher levels of crime in other districts during high-alert periods. From table 4 column1, during periods of high alert, crime in the National Mall area decreases by 2.62 crimes per day. Crime also decreases in the other districts, by .571 crimes per day, but this effect is not statistically significant. 
Conclusion: First, police increase in one district does not decrease police presence in other districts. Second, the difference between the first raw and the second raw shows the difference-in-difference estimator that controls for all common factors between the districts. 


